Software Citation Principles

### 2016-08-04 sc-principles/software-citation-principles.tex

Any opinion, finding, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the NSF.

>>>>

While D.~S.~Katz prepared this material while employed at the NSF, any opinion, finding, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the NSF.
